### 2023-03-12 main/chapter_2ljets.tex
describe region subsets

\begin{figure}[tp]
\centering
\begin{subfigure}{0.7\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\\
\begin{subfigure}{0.7\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although figures were produced before unblinding, with older samples and region
designs, their later updates do not change the general message.
Values of $\cls$ from expected data in the combined fit are overlaid.
}
\label{fig:2ljets_fit_multi_contours}
\end{figure}

>>>>

The signal region subsets whose exclusions are presented in
Figure~\ref{fig:2ljets_fit_multi_contours} are described as follows:
\begin{itemize}
\item `High' contains only the bins of SR-High and SR-High-1J.
\item `HighNo4' contains only the bins of SR-High only.
It excludes SR-High-1J such that the difference between `High' and `HighNo4'
evaluates the impact of including the mono-jet region SR-High-1J.
\item `$\llbb$' contains only SR-$\llbb$.
It is not independently sensitive to the C1N2 models, but demonstrates the
unique reach gained by SR-$\llbb$ for GMSB models.
\item `Int' contains only the bins of SR-Int.
\item `Low` contains only the bins of SR-Low.
\item `OffShell` contains only the bins of SR-OffShell.
\end{itemize}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.7\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\\
\begin{subfigure}{0.7\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although these figures were produced before unblinding, with older samples and
region designs, their later updates do not change the general message.
Values of $\cls$ from expected data in the combined fit are overlaid in tiny
grey text.
}
\label{fig:2ljets_fit_multi_contours}
\end{figure}
